Gafo-cc visuals

### 2022-07-20 analysis/gafo-cc-visuals.Rmd
prep hier model run

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "glm")+
  scale_color_colorblind(name = "", labels = c("Nigeria", "Namibia", "Sambia", "Namibia", "Germany"))+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()+
  theme(legend.position = "bottom")

>>>>

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "glm")+
  scale_color_colorblind(name = "")+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()+
  theme(legend.position = "bottom")
